---
title: "BarraganEtAl2025_Analysis_Field"
author: "Daan Mertens"
date: "5/24/2023"
output: html_document
---

Markdown document *detailing the analysis of the effects of soil amendment on plant development, the pollinator community, and seed production*, as part of "Bio-residuals of industrial insect production as novel sustainable crop fertilizer". 
Contact info: d.mertens.sci@gmail.com
Please use a "CC BY license" principle: Free to use and adapt, with credit to original author(s) when due.


To make this document concise we only present the selected models, output, and construction of the figures presented in the manuscript or supporting files. We do not present the initial data exploration and model selection steps.

The best fitting model was selected from: 
- Models with Gaussian probability distribution
- Models with Gaussian probability distribution, extended with variance functions to account for heterogeneity of data
Depending on the type of data:
- Models with Gamma (link = log) probability distribution
- Models with Negative binomial, Quasi poisson, or Poisson probability distributions (link = log) 

Models were then compared using AIC and for he model with lowest AIC score we verified whether model assumptions were met. If these models still poorly described the data, we transformed data using a log transformation and reiterated the selection process.

# Set-up environment
```{r, Libraries - Functions}
# Libraries
library(readxl) # Reads data from excel files
library(ggplot2) # Package for plotting
library(gridExtra) # Package for multipanel plotting
library(lme4) # Mixed effect models
library(nlme) # Mixed effect models
library(glmmTMB) # Mixed effect models
library(emmeans) # Estimate marginal means of factors in models
library(car) # Estimate effects in Anova-like tables
library(multcomp) # Calculate post-hoc tests
library(multcompView) # Compact letter display of model results
library(vegan) # Multivariate analysis
library(bipartite) # bipartite interaction networks
library(piecewiseSEM) # Piecewise SEM

# ggplot custom theme for consistent plotting
CustomPlot = list(
  theme(plot.title = element_text(hjust = 0.5),
        axis.text = element_text( color = "black"),
        axis.line = element_line(colour = "black"),
        panel.background = element_rect(fill = NA, colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour = "black", fill = NA),
        strip.text = element_text(colour = "black"),
        legend.key = element_rect(fill = NA, color = NA))
)

# Easy 'not in' function to subset
`%notin%` <- Negate(`%in%`)

# Set a vector with treatment colors. 
Treatment.colours <- c("#8A9197FF", 
                       "#014d64",
                       "#3B9AB2",
                       "#7ad2f6",
                       "#EBCC2A",
                       "#D55E00")
```
#_
# A. Plant development in Field

Analysis of the data on plant development collected in the field experiments of 2021 and 2021. 

# 1. Data
```{r, Field data}
# Data
Data2020 <- read_excel("../Data/Field_2020_2021.xlsx", sheet = "2020")
Data2021 <- read_excel("../Data/Field_2020_2021.xlsx", sheet = "2021")

# Set unique block codes for 2021 and 2021
Data2020$Block_Code <- paste(Data2020$Block,"20", sep = "") 
Data2021$Block_Code <- paste(Data2021$Block,"21", sep = "") 

# Add an identifier for the year, and combine the data sets
Data2020$Year <- 2020
Data2021$Year <- 2021

Field.Data <- rbind(Data2020,Data2021)

# Set appropriate columns to factor levels
Factors <- c("Plant_Code","Treatment","Block", "Block_Code", "Year")
Field.Data[Factors] <- lapply(Field.Data[Factors], factor)

# Specify the order of levels for consistent plotting and color matching
Field.Data$Treatment <- factor(Field.Data$Treatment, levels = c("C", "HC", "BSF", "MW", "CHT", "OF"))
```

# 2. Univariate analysis

We fit an interaction model including the soil amendment treatments and the year in which the experiment was conducted (Response \~ Treatment \* Year), including the block in which plants were planted as random intercept to account for dependency of our data. We then assess the overall effect of the fixed factors in the model by performing a Type II Wald's Chi-square test. Finally, we perform a *post-hoc* analysis (Tukey HSD) conditional on each of the two years, and construct figures.

## 2.1 Plant height T1
```{r, Plant height T1}
# Subset data, remove unmeasured plants
HeightT1.data <- na.omit(Field.Data[,c("Treatment", "Year", "Block_Code", "Plant_Code", "HeightT1")])
# Best fitting model 
M.HeightT1 <- lme(HeightT1 ~ Treatment * Year, 
                        random = ~1|Block_Code,
                        weights = varComb(varIdent(form = ~ 1 | Treatment), 
                                            varIdent(form = ~ 1 | Year)),
                        method = "REML",
                        na.action = na.exclude,
                        data = HeightT1.data) 


# Wald Chi-square test 
Anova(M.HeightT1)

# Post-hoc analysis
PostHoc.HeightT1 <- emmeans(M.HeightT1, pairwise ~ Treatment|Year)
CLD.M.HeightT1 <- data.frame(cld(PostHoc.HeightT1$emmeans,Letters = letters))

# Figure
ggplot(HeightT1.data, aes(x = Treatment, y = HeightT1, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.M.HeightT1, aes(x = Treatment, 
                                      y = max(HeightT1.data$HeightT1) + 5 , 
                                      label = .group), 
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "Height at T1") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot

```

## 2.2 Plant height T2
```{r, Plant height T2}
# Subset data, remove unmeasured plants
HeightT2.data <- na.omit(Field.Data[,c("Treatment", "Year", "Block_Code", "Plant_Code", "HeightT2")])

# Best fitting model 
M.HeightT2 <- lme(HeightT2 ~ Treatment * Year, 
                        random = ~1|Block_Code,
                        weights = varIdent(form = ~ 1 | Year),
                        method = "REML",
                        na.action = na.exclude,
                        data = HeightT2.data) 

# Wald Chi-square test 
Anova(M.HeightT2)

# Post-hoc analysis
PostHoc.HeightT2 <- emmeans(M.HeightT2, pairwise ~ Treatment|Year)
CLD.M.HeightT2 <- data.frame(cld(PostHoc.HeightT2$emmeans,Letters = letters))

# Figure
ggplot(HeightT2.data, aes(x = Treatment, y = HeightT2, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.M.HeightT2, aes(x = Treatment, 
                                      y = max(HeightT2.data$HeightT2) + 15 , 
                                      label = .group), 
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "Height at T2") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 110)) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot

```

## 2.3 Plant width T1
```{r, Plant width T1}
# Subset data, remove unmeasured plants
WidthT1.data <- na.omit(Field.Data[,c("Treatment", "Year", "Block_Code", "Plant_Code", "WidthT1")])

# Best fitting model 
M.WidthT1 <- lme(WidthT1 ~ Treatment * Year,
                 random = ~1|Block_Code, 
                 weights = varComb(varIdent(form = ~ 1 | Treatment),
                                   varIdent(form = ~ 1 | Year)),
                 method = "REML",
                 na.action = na.exclude,
                 data = WidthT1.data) 
                     
# Wald Chi-square test 
Anova(M.WidthT1)

# Post-hoc analysis
PostHoc.WidthT1 <- emmeans(M.WidthT1, pairwise ~ Treatment|Year)
CLD.M.WidthT1 <- data.frame(cld(PostHoc.WidthT1$emmeans,Letters = letters))

# Figure
ggplot(WidthT1.data, aes(x = Treatment, y = WidthT1, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.M.WidthT1, aes(x = Treatment, 
                                      y = max(WidthT1.data$WidthT1) + 4 , 
                                      label = .group), 
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "Width at T1") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 40)) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot

```

## 2.4 Plant width T2
```{r, Plant width T2}
# Subset data, remove unmeasured plants
WidthT2.data <- na.omit(Field.Data[,c("Treatment", "Year", "Block_Code", "Plant_Code", "WidthT2")])

# Best fitting model 
M.WidthT2 <- lme(WidthT2 ~ Treatment * Year, 
                 random = ~1|Block_Code,
                 weights = varIdent(form = ~ 1 | Year),
                 method = "REML",
                 na.action = na.exclude,
                 data = WidthT2.data)

# Wald Chi-square test 
Anova(M.WidthT2)

# Post-hoc analysis
PostHoc.WidthT2 <- emmeans(M.WidthT2, pairwise ~ Treatment|Year)
CLD.M.WidthT2 <- data.frame(cld(PostHoc.WidthT2$emmeans,Letters = letters))

# Figure
ggplot(WidthT2.data, aes(x = Treatment, y = WidthT2, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.M.WidthT2, aes(x = Treatment, 
                                      y = max(WidthT2.data$WidthT2) + 5 , 
                                      label = .group), 
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "Width at T2") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 65)) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot

```

##  2.5 Number of flowers T1
```{r, Number of flowers T1}
# Subset data, remove unmeasured plants
NFlowerT1.data <- na.omit(Field.Data[,c("Treatment", "Year", "Block_Code", "Plant_Code", "NflowT1")])

# Exploration and initial analysis showed that log transformation was necessary for regression analysis
NFlowerT1.data$NflowT1 <- log(NFlowerT1.data$NflowT1)

# Best fitting model 
M.NFlowerT1 <- lme(NflowT1 ~ Treatment * Year,
                   random = ~1|Block_Code,
                   weights = varIdent(form = ~ 1 | Year),
                   method = "REML",
                   na.action = na.exclude,
                   data = NFlowerT1.data)
                     
# Wald Chi-square test 
Anova(M.NFlowerT1)

# Post-hoc analysis
PostHoc.NFlowerT1 <- emmeans(M.NFlowerT1, pairwise ~ Treatment|Year)
CLD.M.NFlowerT1 <- data.frame(cld(PostHoc.NFlowerT1$emmeans,Letters = letters))

# Figure
ggplot(NFlowerT1.data, aes(x = Treatment, y = NflowT1, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.M.NFlowerT1, aes(x = Treatment, 
                                      y = max(NFlowerT1.data$NflowT1) + 1 , 
                                      label = .group), 
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "log (Number of flowers) at T1") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 8)) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot

```

## 2.6 Number of flowers T2
```{r, Number of flowers T2}
# Subset data, remove unmeasured plants
NFlowerT2.data <- na.omit(Field.Data[,c("Treatment", "Year", "Block_Code", "Plant_Code", "NflowT2")])

# Exploration and initial analysis showed that log transformation was necessary for regression analysis
NFlowerT2.data$NflowT2 <- log(NFlowerT2.data$NflowT2)

# Best fitting model 
M.NFlowerT2 <- lme(NflowT2 ~ Treatment * Year,
                   random = ~1|Block_Code,
                   weights = varComb(varIdent(form = ~ 1 | Treatment), 
                                     varIdent(form = ~ 1 | Year)),
                   method = "REML",
                   na.action = na.exclude,
                   data = NFlowerT2.data)

# Wald Chi-square test 
Anova(M.NFlowerT2)

# Post-hoc analysis
PostHoc.NFlowerT2 <- emmeans(M.NFlowerT2, pairwise ~ Treatment|Year)
CLD.M.NFlowerT2 <- data.frame(cld(PostHoc.NFlowerT2$emmeans,Letters = letters))

# Figure
ggplot(NFlowerT2.data, aes(x = Treatment, y = NflowT2, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.M.NFlowerT2, aes(x = Treatment, 
                                      y = max(NFlowerT2.data$NflowT2) + 1.2 , 
                                      label = .group), 
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "log (Number of flowers) at T2") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 9)) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot

```

## 2.7 Days until flowering
```{r, Days until flowering}
# Subset data, remove unmeasured plants
SowToFlower.data <- na.omit(Field.Data[,c("Treatment", "Year", "Block_Code", "Plant_Code", "Sow_To_Flower")])

# Exploration and initial analysis showed that log transformation was necessary for regression analysis
SowToFlower.data$Sow_To_Flower <- log(SowToFlower.data$Sow_To_Flower)

# Best fitting model 
M.SowToFlower <- lme(Sow_To_Flower ~ Treatment * Year,
                     random = ~1|Block_Code,
                     weights =  varIdent(form = ~ 1 | Year),
                     method = "REML",
                     na.action = na.exclude,
                     data = SowToFlower.data)

# Wald Chi-square test 
Anova(M.SowToFlower)

# Post-hoc analysis
PostHoc.SowToFlower <- emmeans(M.SowToFlower, pairwise ~ Treatment|Year)
CLD.M.SowToFlower <- data.frame(cld(PostHoc.SowToFlower$emmeans,Letters = letters))

# Figure
ggplot(SowToFlower.data, aes(x = Treatment, y = Sow_To_Flower, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.M.SowToFlower, aes(x = Treatment, 
                                      y = max(SowToFlower.data$Sow_To_Flower) + 0.5 , 
                                      label = .group), 
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "log (Days until flowring)") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 5)) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot

```

## 2.8 Seed set
```{r, Seed set}
# Select data, remove plants which did not reproduce
Seedset.data <- na.omit(Field.Data[,c("Treatment", "Year", "Block_Code", "Plant_Code", "Nseeds")])

# Exploration and initial analysis showed that log transformation was necessary for regression analysis
Seedset.data$Nseeds <- log(Seedset.data$Nseeds)

# Best fitting model 
M.Seedset <- lme(Nseeds ~ Treatment * Year, 
                          random = ~1|Block_Code, 
                          weights = varComb(varIdent(form = ~ 1 | Treatment), 
                                            varIdent(form = ~ 1 | Year)),
                          method = "REML",
                          data = Seedset.data)

# Wald Chi-square test 
Anova(M.Seedset)

# Post-hoc analysis
PostHoc.Seedset <- emmeans(M.Seedset, pairwise ~ Treatment|Year)
CLD.M.Seedset <- data.frame(cld(PostHoc.Seedset$emmeans,Letters = letters))

# Figure
ggplot(Seedset.data, aes(x = Treatment, y = Nseeds, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.M.Seedset, aes(x = Treatment, 
                                      y = max(Seedset.data$Nseeds) + 1 , 
                                      label = .group), 
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "log (Number of seeds)") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 13) ) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot

```

# 3. Multivariate analysis

Here, we use ordination to represent variation in plant development among treatments in multivariate space. We then apply non-parametric multivariate analysis of variance (PERMANOVA) to test if treatments significantly explain (part of) the variation in our data. Finally, we assess pairwise differences between the different treatments by comparing subsets of the data and adjusting the p-values obtained by PERMANOVA using false-discovery rates.

## 3.1 PCA Ordination 
### 3.1.1 PCA T1 2020
```{r, PCA T1 2020}
# Subset and transform data to match regression analysis
Field.Data.2020 <- subset(Field.Data, Year == 2020)

Field.Data.2020_T1 <- na.omit(Field.Data.2020[,c("Treatment",
                                                 "Year",
                                                 "Block",
                                                 "Plant_Code",
                                                 "WidthT1",
                                                 "HeightT1",
                                                 "NflowT1",
                                                 "Sow_To_Flower")])

Field.Data.2020_T1$NflowT1 <- log(Field.Data.2020_T1$NflowT1)
Field.Data.2020_T1$Sow_To_Flower <- log(Field.Data.2020_T1$Sow_To_Flower)
# Scale variables to mean = 0 and SD = 1
Field.Data.2020_T1_Scaled <- data.frame(Field.Data.2020_T1[,c(1:4)], scale(Field.Data.2020_T1[,5:8]))

# Calculate PCA
PCA_T1_2020 <- rda(Field.Data.2020_T1_Scaled[,c(5:8)])

# Extract scores to calculate centroids and plotting
Coordinates_T1_2020 <- summary(PCA_T1_2020)$sites
Annotated_Coordinates_T1_2020 <- cbind(Field.Data.2020_T1_Scaled[1:4],Coordinates_T1_2020)
Traits_T1_2020 <- as.data.frame(summary(PCA_T1_2020)$species)

# Calculate centroids
PC1.Centroid <- as.data.frame(emmeans(lm(PC1 ~ Treatment, data = Annotated_Coordinates_T1_2020), ~ Treatment))
PC2.Centroid <- as.data.frame(emmeans(lm(PC2 ~ Treatment, data = Annotated_Coordinates_T1_2020), ~ Treatment))

Centroids_T1_2020 <- data.frame("Treatment" = c("C","HC","BSF","MW","CHT","OF"),
                                "PC1" = as.vector(PC1.Centroid$emmean),
                                "SE1" = as.vector(PC1.Centroid$SE),
                                "PC2" = as.vector(PC2.Centroid$emmean),
                                "SE2" = as.vector(PC2.Centroid$SE))

Centroids_T1_2020$Treatment <- factor(Centroids_T1_2020$Treatment, levels = c("C", "HC", "BSF", "MW", "CHT", "OF"))
```

### 3.1.2  PCA T1 2021
```{r, PCA T1 2021}
# Subset and transform data to match regression analysis
Field.Data.2021 <- subset(Field.Data, Year == 2021)

Field.Data.2021_T1 <- na.omit(Field.Data.2021[,c("Treatment",
                                                 "Year",
                                                 "Block",
                                                 "Plant_Code",
                                                 "WidthT1",
                                                 "HeightT1",
                                                 "NflowT1",
                                                 "Sow_To_Flower")])

Field.Data.2021_T1$NflowT1 <- log(Field.Data.2021_T1$NflowT1)
Field.Data.2021_T1$Sow_To_Flower <- log(Field.Data.2021_T1$Sow_To_Flower)

# Scale variables to mean = 0 and SD = 1
Field.Data.2021_T1_Scaled <- data.frame(Field.Data.2021_T1[,c(1:4)], scale(Field.Data.2021_T1[,5:8]))

# Calculate PCA
PCA_T1_2021 <- rda(Field.Data.2021_T1_Scaled[,c(5:8)])

# Extract scores to calculate centroids and plotting
Coordinates_T1_2021 <- summary(PCA_T1_2021)$sites
Annotated_Coordinates_T1_2021 <- cbind(Field.Data.2021_T1_Scaled[1:4],Coordinates_T1_2021)
Traits_T1_2021 <- as.data.frame(summary(PCA_T1_2021)$species)

# Calculate centroids
PC1.Centroid <- as.data.frame(emmeans(lm(PC1 ~ Treatment, data = Annotated_Coordinates_T1_2021), ~ Treatment))
PC2.Centroid <- as.data.frame(emmeans(lm(PC2 ~ Treatment, data = Annotated_Coordinates_T1_2021), ~ Treatment))

Centroids_T1_2021 <- data.frame("Treatment" = c("C","HC","BSF","MW","CHT","OF"),
                                "PC1" = as.vector(PC1.Centroid$emmean),
                                "SE1" = as.vector(PC1.Centroid$SE),
                                "PC2" = as.vector(PC2.Centroid$emmean),
                                "SE2" = as.vector(PC2.Centroid$SE))

Centroids_T1_2021$Treatment <- factor(Centroids_T1_2021$Treatment, levels = c("C", "HC", "BSF", "MW", "CHT", "OF"))

```

### 3.1.3 PCA T2 2020
```{r, PCA T2 2020}
# Subset and transform data to match regression analysis
Field.Data.2020 <- subset(Field.Data, Year == 2020)

Field.Data.2020_T2 <- na.omit(Field.Data.2020[,c("Treatment",
                                                 "Year",
                                                 "Block",
                                                 "Plant_Code",
                                                 "WidthT2",
                                                 "HeightT2",
                                                 "NflowT2")])

Field.Data.2020_T2$NflowT2 <- log(Field.Data.2020_T2$NflowT2)

# Scale variables to mean = 0 and SD = 1
Field.Data.2020_T2_Scaled <- data.frame(Field.Data.2020_T2[,c(1:4)], scale(Field.Data.2020_T2[,5:7]))

# Calculate PCA
PCA_T2_2020 <- rda(Field.Data.2020_T2_Scaled[,c(5:7)])

# Extract scores to calculate centroids and plotting
Coordinates_T2_2020 <- summary(PCA_T2_2020)$sites
Annotated_Coordinates_T2_2020 <- cbind(Field.Data.2020_T2_Scaled[1:4],Coordinates_T2_2020)
Traits_T2_2020 <- as.data.frame(summary(PCA_T2_2020)$species)

# Calculate centroids
PC1.Centroid <- as.data.frame(emmeans(lm(PC1 ~ Treatment, data = Annotated_Coordinates_T2_2020), ~ Treatment))
PC2.Centroid <- as.data.frame(emmeans(lm(PC2 ~ Treatment, data = Annotated_Coordinates_T2_2020), ~ Treatment))

Centroids_T2_2020 <- data.frame("Treatment" = c("C","HC","BSF","MW","CHT","OF"),
                                "PC1" = as.vector(PC1.Centroid$emmean),
                                "SE1" = as.vector(PC1.Centroid$SE),
                                "PC2" = as.vector(PC2.Centroid$emmean),
                                "SE2" = as.vector(PC2.Centroid$SE))

Centroids_T2_2020$Treatment <- factor(Centroids_T2_2020$Treatment, levels = c("C", "HC", "BSF", "MW", "CHT", "OF"))

```

### 3.1.4 PCA T2 2021
```{r, PCA T2 2021}
# Subset and transform data to match regression analysis
Field.Data.2021 <- subset(Field.Data, Year == 2021)

Field.Data.2021_T2 <- na.omit(Field.Data.2021[,c("Treatment",
                                                 "Year",
                                                 "Block",
                                                 "Plant_Code",
                                                 "WidthT2",
                                                 "HeightT2",
                                                 "NflowT2")])

Field.Data.2021_T2$NflowT2 <- log(Field.Data.2021_T2$NflowT2)

# Scale variables to mean = 0 and SD = 1
Field.Data.2021_T2_Scaled <- data.frame(Field.Data.2021_T2[,c(1:4)], scale(Field.Data.2021_T2[,5:7]))

# Calculate PCA
PCA_T2_2021 <- rda(Field.Data.2021_T2_Scaled[,c(5:7)])

# Extract scores to calculate centroids and plotting
Coordinates_T2_2021 <- summary(PCA_T2_2021)$sites
Annotated_Coordinates_T2_2021 <- cbind(Field.Data.2021_T2_Scaled[1:4],Coordinates_T2_2021)
Traits_T2_2021 <- as.data.frame(summary(PCA_T2_2021)$species)

# Calculate centroids
PC1.Centroid <- as.data.frame(emmeans(lm(PC1 ~ Treatment, data = Annotated_Coordinates_T2_2021), ~ Treatment))
PC2.Centroid <- as.data.frame(emmeans(lm(PC2 ~ Treatment, data = Annotated_Coordinates_T2_2021), ~ Treatment))

Centroids_T2_2021 <- data.frame("Treatment" = c("C","HC","BSF","MW","CHT","OF"),
                                "PC1" = as.vector(PC1.Centroid$emmean),
                                "SE1" = as.vector(PC1.Centroid$SE),
                                "PC2" = as.vector(PC2.Centroid$emmean),
                                "SE2" = as.vector(PC2.Centroid$SE))

Centroids_T2_2021$Treatment <- factor(Centroids_T2_2021$Treatment, levels = c("C", "HC", "BSF", "MW", "CHT", "OF"))

```

### 3.1.4 Plot ordinations
``` {r, Plot ordinations}
Loading_PCA <- vector(mode = "list", length = 4)

Loading_PCA[[1]] <- ggplot() +
  geom_point(data = Annotated_Coordinates_T1_2020, aes(x = PC1, y = PC2, colour = Treatment), alpha = 0.4, show.legend = F) + 
  geom_point(data = Centroids_T1_2020, 
             aes(x = PC1, y = PC2,colour = Treatment), 
             show.legend = F, 
             size = 4,
             shape = 17) +
  geom_segment(data = Traits_T1_2020, 
               aes(x = 0, y = 0, xend = PC1, yend = PC2),
               arrow = arrow(length = unit(0.03,units = "npc"))) +
  geom_text(data = Traits_T1_2020, 
            aes(x = PC1, y = PC2, label = row.names(Traits_T1_2020)),
            check_overlap = TRUE, 
            nudge_x = 0.15, 
            nudge_y = -0.08) +
  labs(title = "2020 Timepoint 1 ",x = "PC1 (39.91%)", y = "PC2 (34.58%)") +
  scale_colour_manual(values = Treatment.colours) +
  CustomPlot

Loading_PCA[[2]] <- ggplot() +
  geom_point(data = Annotated_Coordinates_T1_2021, aes(x = PC1, y = PC2, colour = Treatment), alpha = 0.4, show.legend = F) + 
  geom_point(data = Centroids_T1_2021, 
             aes(x = PC1, y = PC2, colour = Treatment), 
             show.legend = F, 
             size = 4,
             shape = 17) +
  geom_segment(data = Traits_T1_2021, 
               aes(x = 0, y = 0, xend = PC1, yend = PC2),
               arrow = arrow(length = unit(0.03, units = "npc"))) +
  geom_text(data = Traits_T1_2021, 
            aes(x = PC1, y = PC2, label = row.names(Traits_T1_2021)),
            check_overlap = TRUE, 
            nudge_x = 0.05, 
            nudge_y = -0.05) +
  labs(title = "2021 Timepoint 1",x = "PC1 (47.22%)", y = "PC2 (24.87%)") +
  scale_colour_manual(values = Treatment.colours) +
  CustomPlot

Loading_PCA[[3]] <- ggplot() +
  geom_point(data = Annotated_Coordinates_T2_2020, aes(x = PC1, y = PC2, colour = Treatment), alpha = 0.4, show.legend = F) + 
  geom_point(data = Centroids_T2_2020, 
             aes(x = PC1, y = PC2, colour = Treatment), 
             show.legend = F, 
             size = 4,
             shape = 17) +
  geom_segment(data = Traits_T2_2020, 
               aes(x = 0, y = 0, xend = PC1, yend = PC2),
               arrow = arrow(length = unit(0.03,units = "npc"))) +
  geom_text(data = Traits_T2_2020, 
            aes(x = PC1, y = PC2, label = row.names(Traits_T2_2021)),
            check_overlap = TRUE, 
            nudge_x = 0.05, 
            nudge_y = -0.05) +
  labs(title = "2020 Timepoint 2",x = "PC1 (60.00%)", y = "PC2 (24.87%)") +
  scale_colour_manual(values = Treatment.colours) +
  CustomPlot

Loading_PCA[[4]] <- ggplot() +
  geom_point(data = Annotated_Coordinates_T2_2021, aes(x = PC1, y = PC2, colour = Treatment), alpha = 0.4, show.legend = F) + 
  geom_point(data = Centroids_T2_2021,
             aes(x = PC1, y = PC2, colour = Treatment), 
             show.legend = F, 
             size = 4,
             shape = 17) + 
  geom_segment(data = Traits_T2_2021, 
               aes(x = 0, y = 0, xend = PC1, yend = PC2),
               arrow = arrow(length = unit(0.03,units = "npc"))) +
  geom_text(data = Traits_T2_2021, 
            aes(x = PC1, y = PC2, label = row.names(Traits_T2_2021)),
            check_overlap = TRUE, 
            nudge_x = 0.05, 
            nudge_y = -0.05) +
  labs(title = "2021 Timepoint 2",x = "PC1 (69.86%)", y = "PC2 (15.53%)") +
  scale_colour_manual(values = Treatment.colours) +
  CustomPlot

Ordination_Layout <- rbind(c(1,2),c(3,4)) 

Loading_PCA_Plotted <- marrangeGrob(Loading_PCA, nrow = 2, ncol = 2,layout_matrix = Ordination_Layout)
Loading_PCA_Plotted
```
## 3.2 Treatment effects

### 3.2.1 T1 2020
```{r, Permutation T1 2020}
Permutation.Design <- how(nperm = 1000,
                          # Do not shuffle the plants between blocks
                          blocks = Field.Data.2020_T1_Scaled$Block)

(T1_2020 <- adonis2(Field.Data.2020_T1_Scaled[,c(5:8)] ~ Treatment, 
                    data = Field.Data.2020_T1_Scaled, 
                    method = "euclidean",
                    permutations = Permutation.Design))

```

### 3.2.2 T1 2021
```{r, Permutation T1 2021}
Permutation.Design <- how(nperm = 1000,
                          # Do not shuffle the plants between blocks
                          blocks = Field.Data.2021_T1_Scaled$Block)

(T1_2021 <- adonis2(Field.Data.2021_T1_Scaled[,c(5:8)] ~ Treatment, 
                    data = Field.Data.2021_T1_Scaled, 
                    method = "euclidean",
                    permutations = Permutation.Design))

```

### 3.2.3 T2 2020
```{r, Permutation T2 2020}
Permutation.Design <- how(nperm = 1000,
                          # Do not shuffle the plants between blocks
                          blocks = Field.Data.2020_T2_Scaled$Block)

(T2_2020 <- adonis2(Field.Data.2020_T2_Scaled[,c(5:7)] ~ Treatment, 
                    data = Field.Data.2020_T2_Scaled, 
                    method = "euclidean",
                    permutations = Permutation.Design))

```

### 3.2.4 T2 2021
```{r, Permutation T2 2021}
Permutation.Design <- how(nperm = 1000,
                          # Do not shuffle the plants between blocks
                          blocks = Field.Data.2021_T2_Scaled$Block)

(T2_2021 <- adonis2(Field.Data.2021_T2_Scaled[,c(5:7)] ~ Treatment, 
                    data = Field.Data.2021_T2_Scaled, 
                    method = "euclidean",
                    permutations = Permutation.Design))

```

## 3.3 Pairwise comparisons


### 3.3.1 T1_2021
```{r, Pairwise T1_2020}
Different.Treatments <- levels(Field.Data$Treatment)
N_Perm = 1000

T1_2020.Comparisons <-data.frame("Treatment_A" = c(rep("C", 5),
                                                   rep("HC", 4),
                                                   rep("BSF", 3),
                                                   rep("MW", 2),
                                                   "CHT"),
                                 "Treatment_B" = c(Different.Treatments[-1],
                                                   Different.Treatments[3:6],
                                                   Different.Treatments[4:6],
                                                   Different.Treatments[5:6],
                                                   Different.Treatments[6]),
                                 "Pseudo_F" = 1,
                                 "P_Value" = 1)

for(i in 1:(nrow(T1_2020.Comparisons))){
  
  Sub.data <- subset(Field.Data.2020_T1_Scaled, Treatment == c(T1_2020.Comparisons[i,1], 
                                                               T1_2020.Comparisons[i,2]))
  Permutation.Design <- how(nperm = N_Perm,
                            # Do not shuffle the plants between blocks
                            blocks = Sub.data$Block)
  Perm.Comp <- adonis2(Sub.data[,c(5:8)] ~ Treatment, 
                       data = Sub.data, 
                       method = "euclidean",
                       permutations = Permutation.Design)
  
  T1_2020.Comparisons[i,3] <- Perm.Comp$F[1]
  T1_2020.Comparisons[i,4] <- Perm.Comp$`Pr(>F)`[1]
  
}
T1_2020.Comparisons$FDR <- p.adjust(T1_2020.Comparisons$P_Value, method = "fdr")


```

### 3.3.2 T1_2021
```{r, Pairwise T1_2021}
Different.Treatments <- levels(Field.Data$Treatment)
N_Perm = 1000

T1_2021.Comparisons <-data.frame("Treatment_A" = c(rep("C", 5),
                                                   rep("HC", 4),
                                                   rep("BSF", 3),
                                                   rep("MW", 2),
                                                   "CHT"),
                                 "Treatment_B" = c(Different.Treatments[-1],
                                                   Different.Treatments[3:6],
                                                   Different.Treatments[4:6],
                                                   Different.Treatments[5:6],
                                                   Different.Treatments[6]),
                                 "Pseudo_F" = 1,
                                 "P_Value" = 1)

for(i in 1:(nrow(T1_2021.Comparisons))){
  
  Sub.data <- subset(Field.Data.2021_T1_Scaled, Treatment == c(T1_2021.Comparisons[i,1], 
                                                               T1_2021.Comparisons[i,2]))
  Permutation.Design <- how(nperm = N_Perm,
                            # Do not shuffle the plants between blocks
                            blocks = Sub.data$Block)
  Perm.Comp <- adonis2(Sub.data[,c(5:8)] ~ Treatment, 
                       data = Sub.data, 
                       method = "euclidean",
                       permutations = Permutation.Design)
  
  T1_2021.Comparisons[i,3] <- Perm.Comp$F[1]
  T1_2021.Comparisons[i,4] <- Perm.Comp$`Pr(>F)`[1]
  
}
T1_2021.Comparisons$FDR <- p.adjust(T1_2021.Comparisons$P_Value, method = "fdr")

```


### 3.3.3 T2_2020
```{r, Pairwise T2_2020}
Different.Treatments <- levels(Field.Data$Treatment)
N_Perm = 1000

T2_2020.Comparisons <-data.frame("Treatment_A" = c(rep("C", 5),
                                                   rep("HC", 4),
                                                   rep("BSF", 3),
                                                   rep("MW", 2),
                                                   "CHT"),
                                 "Treatment_B" = c(Different.Treatments[-1],
                                                   Different.Treatments[3:6],
                                                   Different.Treatments[4:6],
                                                   Different.Treatments[5:6],
                                                   Different.Treatments[6]),
                                 "Pseudo_F" = 1,
                                 "P_Value" = 1)

for(i in 1:(nrow(T2_2020.Comparisons))){
  
  Sub.data <- subset(Field.Data.2020_T2_Scaled, Treatment == c(T2_2020.Comparisons[i,1], 
                                                               T2_2020.Comparisons[i,2]))
  Permutation.Design <- how(nperm = N_Perm,
                            # Do not shuffle the plants between blocks
                            blocks = Sub.data$Block)
  Perm.Comp <- adonis2(Sub.data[,c(5:7)] ~ Treatment, 
                       data = Sub.data, 
                       method = "euclidean",
                       permutations = Permutation.Design)
  
  T2_2020.Comparisons[i,3] <- Perm.Comp$F[1]
  T2_2020.Comparisons[i,4] <- Perm.Comp$`Pr(>F)`[1]
  
}
T2_2020.Comparisons$FDR <- p.adjust(T2_2020.Comparisons$P_Value, method = "fdr")

```

### 3.3.4 T2_2021
```{r, Pairwise T2_2021}
Different.Treatments <- levels(Field.Data$Treatment)
N_Perm = 1000

T2_2021.Comparisons <-data.frame("Treatment_A" = c(rep("C", 5),
                                                   rep("HC", 4),
                                                   rep("BSF", 3),
                                                   rep("MW", 2),
                                                   "CHT"),
                                 "Treatment_B" = c(Different.Treatments[-1],
                                                   Different.Treatments[3:6],
                                                   Different.Treatments[4:6],
                                                   Different.Treatments[5:6],
                                                   Different.Treatments[6]),
                                 "Pseudo_F" = 1,
                                 "P_Value" = 1)

for(i in 1:(nrow(T2_2021.Comparisons))){
  
  Sub.data <- subset(Field.Data.2021_T2_Scaled, Treatment == c(T2_2021.Comparisons[i,1], 
                                                               T2_2021.Comparisons[i,2]))
  Permutation.Design <- how(nperm = N_Perm,
                            # Do not shuffle the plants between blocks
                            blocks = Sub.data$Block)
  Perm.Comp <- adonis2(Sub.data[,c(5:7)] ~ Treatment, 
                       data = Sub.data, 
                       method = "euclidean",
                       permutations = Permutation.Design)
  
  T2_2021.Comparisons[i,3] <- Perm.Comp$F[1]
  T2_2021.Comparisons[i,4] <- Perm.Comp$`Pr(>F)`[1]
  
}
T2_2021.Comparisons$FDR <- p.adjust(T2_2021.Comparisons$P_Value, method = "fdr")

```

#_
# B. Pollinators

Analysis of the pollinator data collected in the field experiment in seasons 2020 and 2021.

# 1. Data
```{r, Pollinator Data}
# Data
Data2021 <- read_excel("Field_2020_2021.xlsx", sheet = "2020")
Data2021 <- read_excel("Field_2020_2021.xlsx", sheet = "2021")

# Set unique block codes for 2021 and 2021
Data2021$Block_Code <- paste(Data2020$Block,"20", sep = "") 
Data2021$Block_Code <- paste(Data2021$Block,"21", sep = "") 

# Add an identifier for the year, and combine the data sets
Data2021$Year <- 2020
Data2021$Year <- 2021

Field.Data <- rbind(Data2020,Data2021)

# Set appropriate columns to factor levels
Factors <- c("Plant_Code","Treatment","Block", "Block_Code", "Year")
Field.Data[Factors] <- lapply(Field.Data[Factors], factor)

# Specify the order of levels for consistent plotting and color matching
Field.Data$Treatment <- factor(Field.Data$Treatment, levels = c("C", "HC", "BSF", "MW", "CHT", "OF"))

# Select the pollinator data
Pollinator.Data <-  na.omit(Field.Data[,c("Treatment", "Year", "Block_Code", 
                                          "Plant_Code", "TotalPollinators", "FPP")])


```

# 2. Total number of pollinators
```{r, N_Pollinators}
# Best fitting model 
M.TotalPollinators <- glmmTMB(TotalPollinators ~ Treatment * Year + (1|Block_Code),
                              family = Gamma(link = "log"),
                              data = Pollinator.Data)

# Wald Chi-square test 
Anova(M.TotalPollinators)

# Post-hoc analysis
Post.hoc.TotalPollinators <- emmeans(M.TotalPollinators, pairwise ~ Treatment|Year, type = "response")
CLD.TotalPollinators <- data.frame(cld(Post.hoc.TotalPollinators$emmeans,Letters = letters))

# Figure
ggplot(data = Pollinator.Data, 
       aes(x = Treatment, y = TotalPollinators, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.TotalPollinators, 
            aes(x = Treatment, y = max(na.omit(Pollinator.Data$TotalPollinators)) + 5 ,label = .group),
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "Total number of Pollinators") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 70) ) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot

```

# 3. Flower visits per pollinator
```{r, FPP}
# Exploration and initial analysis showed that log transformation was necessary for regression analysis
Pollinator.Data$FPP <- log(Pollinator.Data$FPP)

# Best fitting model 
M.FPP <- lme(FPP ~ Treatment * Year,
             random = ~1|Block_Code, 
             weights = varComb(varIdent(form = ~ 1 | Treatment), varIdent(form = ~ 1 | Year)),
             method = "REML",
             na.action = na.exclude,
             data = Pollinator.Data)

# Wald Chi-square test 
Anova(M.FPP)

# Post-hoc analysis
Post.hoc.FPP <- emmeans(M.FPP, pairwise ~ Treatment|Year, type = "response")
CLD.FPP <- data.frame(cld(Post.hoc.FPP$emmeans,Letters = letters))

# Figure
ggplot(data = Pollinator.Data, 
       aes(x = Treatment, y = FPP, fill = Treatment, colour = Treatment)) +
  facet_wrap(~Year) + 
  geom_boxplot(aes(alpha = 0.3), colour = "black", outlier.shape = 0, outlier.colour = "white") +
  geom_jitter (width = 0.25, height = 0, size = 1) +
  geom_text(data = CLD.FPP, 
            aes(x = Treatment, y = max(na.omit(Pollinator.Data$FPP)) + 0.5 ,label = .group),
            colour = 'black') +
  scale_fill_manual(values = Treatment.colours) +
  scale_colour_manual(values = Treatment.colours) +
  labs(y = "log(Number of flowers visited per pollinator)") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 4) ) +
  guides(alpha = "none", shape = "none", colour = "none", fill = "none") +
  CustomPlot


```

# 4. Interaction networks

```{r, interaction networks data wrangling}
# Select the pollinator data
Pollinator.Groups <-  Field.Data[,c("Treatment", "Year", "Block","Plant_Code",
                                            "Tsyrphid","TOFlies","THBee","TSBee", "TBBee",
                                            "Tsyrphid2","TOFlies2","THBee2","TSBee2", "TBBee2")]

# Subset 2020
Pollinator.Groups.2020 <- subset(Pollinator.Groups, Year == 2020)

# Subset 2020 observation round 1
Pollinator.Groups.2020_T1 <- na.omit(Pollinator.Groups.2020[,c("Treatment",
                                                 "Year",
                                                 "Block",
                                                 "Plant_Code",
                                                 "Tsyrphid",
                                                 "TOFlies",
                                                 "THBee",
                                                 "TSBee", 
                                                 "TBBee")])

# Subset 2020 observation round 2
Pollinator.Groups.2020_T2 <- na.omit(Pollinator.Groups.2020[,c("Treatment",
                                                 "Year",
                                                 "Block",
                                                 "Plant_Code",
                                                 "Tsyrphid2",
                                                 "TOFlies2",
                                                 "THBee2",
                                                 "TSBee2", 
                                                 "TBBee2")])
                                     
# Subset 2021
Pollinator.Groups.2021 <- subset(Pollinator.Groups, Year == 2021)

# Subset 2021 observation round 1
Pollinator.Groups.2021_T1 <- na.omit(Pollinator.Groups.2021[,c("Treatment",
                                                 "Year",
                                                 "Block",
                                                 "Plant_Code",
                                                 "Tsyrphid",
                                                 "TOFlies",
                                                 "THBee",
                                                 "TSBee", 
                                                 "TBBee")])

# Subset 2021 observation round 2
Pollinator.Groups.2021_T2 <- na.omit(Pollinator.Groups.2021[,c("Treatment",
                                                 "Year",
                                                 "Block",
                                                 "Plant_Code",
                                                 "Tsyrphid2",
                                                 "TOFlies2",
                                                 "THBee2",
                                                 "TSBee2", 
                                                 "TBBee2")])

```

Construct bipartite interaction networks

```{r, interaction network plots}
# _ Year 1 - T1 ----
# Number of plants
N_Plants <- table(Pollinator.Groups.2020_T1$Treatment)

# Number of observations in each of the treatments
Agg.Pollinator.Groups.2020_T1 <- aggregate(Pollinator.Groups.2020_T1[,5:9], 
                                           by = list(Pollinator.Groups.2020_T1$Treatment), 
                                           FUN = sum)


# Average number of observations per plant in each treatment
Agg.Pollinator.Groups.2020_T1_REL <-  Agg.Pollinator.Groups.2020_T1[,2:6] / N_Plants

# Set rownames
row.names(Agg.Pollinator.Groups.2020_T1_REL) <-  Agg.Pollinator.Groups.2020_T1$Group.1

# Adjust the column names
colnames(Agg.Pollinator.Groups.2020_T1_REL) <- c("Syrphid flies", 
                                             "Other flies", 
                                             "Honey bees", 
                                             "Solitary bees", 
                                             "Bumblebees")

# Set a vector with colours for the Pollinators 
Pollinator.colours <- c("#f6412d", # Syrphids
                        "#ff5607", # Other flies
                        "#ff9800", # Honeybees
                        "#ffc100", # Solitary bees
                        "#ffec19") # Bumblebees

# Set a vector with colours for the Interactions 
Interaction.colours <- adjustcolor (Pollinator.colours, # Use the same colours as those for the pollinators
                                    alpha.f = 0.5) # Interactions are transparent


# Plot the  network
plotweb(Agg.Pollinator.Groups.2020_T1_REL,
        method = "normal", # Takes the order of treatments and pollinators as it is given in the data frame
        col.low = Treatment.colours, # Colours the boxes of the treatments
        col.high = Pollinator.colours, # Colours the boxes of the pollinators
        col.interaction = Interaction.colours, # Colours the interaction lines
        ybig = 1.2, # Makes the space between upper and lower boxes a bit smaller
        bor.col.interaction = NA, # Remove the black border color
        bor.col.high = NA, # Remove the black border color
        bor.col.low = NA,  # Remove the black border color
        text.rot = 0) # Rotate the labels 90 degrees

# _ Year 2 - T1 ----
# Number of plants
N_Plants <- table(Pollinator.Groups.2021_T1$Treatment)

# Number of observations in each of the treatments
Agg.Pollinator.Groups.2021_T1 <- aggregate(Pollinator.Groups.2021_T1[,5:9], 
                                           by = list(Pollinator.Groups.2021_T1$Treatment), 
                                           FUN = sum)


# Average number of observations per plant in each treatment
Agg.Pollinator.Groups.2021_T1_REL <-  Agg.Pollinator.Groups.2021_T1[,2:6] / N_Plants

# Set rownames
row.names(Agg.Pollinator.Groups.2021_T1_REL) <-  Agg.Pollinator.Groups.2021_T1$Group.1

# Adjust the column names
colnames(Agg.Pollinator.Groups.2021_T1_REL) <- c("Syrphid flies", 
                                                 "Other flies", 
                                                 "Honey bees", 
                                                 "Solitary bees", 
                                                 "Bumblebees")


# Plot the network
plotweb(Agg.Pollinator.Groups.2021_T1_REL,
        method = "normal", # Takes the order of treatments and pollinators as it is given in the data frame
        col.low = Treatment.colours, # Colours the boxes of the treatments
        col.high = Pollinator.colours, # Colours the boxes of the pollinators
        col.interaction = Interaction.colours, # Colours the interaction lines
        ybig = 1.2, # Makes the space between upper and lower boxes a bit smaller
        bor.col.interaction = NA, # Remove the black border color
        bor.col.high = NA, # Remove the black border color
        bor.col.low = NA,  # Remove the black border color
        text.rot = 0) # Rotate the labels 90 degrees



# _ Year 1 - T2 ----
# Number of plants
N_Plants <- table(Pollinator.Groups.2020_T2$Treatment)

# Number of observations in each of the treatments
Agg.Pollinator.Groups.2020_T2 <- aggregate(Pollinator.Groups.2020_T2[,5:9], 
                                           by = list(Pollinator.Groups.2020_T2$Treatment), 
                                           FUN = sum)


# Average number of observations per plant in each treatment
Agg.Pollinator.Groups.2020_T2_REL <-  Agg.Pollinator.Groups.2020_T2[,2:6] / N_Plants

# Set rownames
row.names(Agg.Pollinator.Groups.2020_T2_REL) <-  Agg.Pollinator.Groups.2020_T2$Group.1

# Adjust the column names
colnames(Agg.Pollinator.Groups.2020_T2_REL) <- c("Syrphid flies", 
                                                 "Other flies", 
                                                 "Honey bees", 
                                                 "Solitary bees", 
                                                 "Bumblebees")


# Plot the network
plotweb(Agg.Pollinator.Groups.2020_T2_REL,
        method = "normal", # Takes the order of treatments and pollinators as it is given in the data frame
        col.low = Treatment.colours, # Colours the boxes of the treatments
        col.high = Pollinator.colours, # Colours the boxes of the pollinators
        col.interaction = Interaction.colours, # Colours the interaction lines
        ybig = 1.2, # Makes the space between upper and lower boxes a bit smaller
        bor.col.interaction = NA, # Remove the black border color
        bor.col.high = NA, # Remove the black border color
        bor.col.low = NA,  # Remove the black border color
        text.rot = 0) # Rotate the labels 90 degrees

# _ Year 2 - T2 ----
# Number of plants
N_Plants <- table(Pollinator.Groups.2021_T2$Treatment)

# Number of observations in each of the treatments
Agg.Pollinator.Groups.2021_T2 <- aggregate(Pollinator.Groups.2021_T2[,5:9], 
                                           by = list(Pollinator.Groups.2021_T2$Treatment), 
                                           FUN = sum)


# Average number of observations per plant in each treatment
Agg.Pollinator.Groups.2021_T2_REL <-  Agg.Pollinator.Groups.2021_T2[,2:6] / N_Plants

# Set rownames
row.names(Agg.Pollinator.Groups.2021_T2_REL) <-  Agg.Pollinator.Groups.2021_T2$Group.1

# Adjust the column names
colnames(Agg.Pollinator.Groups.2021_T2_REL) <- c("Syrphid flies", 
                                                 "Other flies", 
                                                 "Honey bees", 
                                                 "Solitary bees", 
                                                 "Bumblebees")


# Plot the network
plotweb(Agg.Pollinator.Groups.2021_T2_REL,
        method = "normal", # Takes the order of treatments and pollinators as it is given in the data frame
        col.low = Treatment.colours, # Colours the boxes of the treatments
        col.high = Pollinator.colours, # Colours the boxes of the pollinators
        col.interaction = Interaction.colours, # Colours the interaction lines
        ybig = 1.2, # Makes the space between upper and lower boxes a bit smaller
        bor.col.interaction = NA, # Remove the black border color
        bor.col.high = NA, # Remove the black border color
        bor.col.low = NA,  # Remove the black border color
        text.rot = 0) # Rotate the labels 90 degrees
```

#_
# C. SEM analysis

Overview of the structural equation models fitted to the data. To make this document concise we do not present the initial exploration, model selection, and model validation steps needed to specify the causal relations within the SEM. We then proceed by estimating the total effects of each variable included in the SEM on seed production.

To calculate the total effects of variables in the SEM on seed production, we need to calculate and sum it's component effects (the direct effect and indirect effect). These component effects should be calculated using the standardized path estimates returned when fitting the SEM. However, PSEM has a known bug where it fails to return standardized path coefficients when component models are fitted with a probability distribution that is not Gaussian (https://github.com/jslefche/piecewiseSEM/issues/232). We therefore used the best fitting GLS models as component models of the SEM

# 1. Data
```{r, SEM Data}
# Data
Data2020 <- read_excel("Field_2020_2021.xlsx", sheet = "2020")
Data2021 <- read_excel("Field_2020_2021.xlsx", sheet = "2021")

# Set unique block codes for 2021 and 2021
Data2020$Block_Code <- paste(Data2020$Block,"20", sep = "") 
Data2021$Block_Code <- paste(Data2021$Block,"21", sep = "") 

# Add an identifier for the year, and combine the data sets
Data2020$Year <- 2020
Data2021$Year <- 2021

Field.Data <- rbind(Data2020,Data2021)

# Set appropriate columns to factor levels
Factors <- c("Plant_Code","Treatment","Block", "Block_Code", "Year")
Field.Data[Factors] <- lapply(Field.Data[Factors], factor)

# Specify the order of levels for consistent plotting and color matching
Field.Data$Treatment <- factor(Field.Data$Treatment, levels = c("C", "HC", "BSF", "MW", "CHT", "OF"))

SEM_Variables <- c("Plant_Code"
  ,"Block_Code"
  , "WidthT1"
  , "WidthT2"
  , "NflowT1"
  , "NflowT2"
  , "HeightT1"
  , "HeightT2"
  , "Sow_To_Flower"
  , "TotalPollinators"
  , "FPP"
  , "Nseeds"
  , "Treatment"
  , "Year")

# Remove plants for which we don't have all observations
SEM.Data <- na.omit(Field.Data[, SEM_Variables])

# Some data transformations are needed. This matches the regression analyses we performed before.
Transformations <- c("NflowT1","NflowT2","Sow_To_Flower", "FPP", "Nseeds")
SEM.Data[Transformations] <- lapply(SEM.Data[Transformations], log)

table(SEM.Data$Treatment)

```

# 2. Causal hypothesis
## 2.1 Overall

```{r, Overall causal hypothesis}
Causal.H <- psem(
  # M1
  lme(Sow_To_Flower ~ WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = SEM.Data),
  
  # M2
  lme(NflowT1 ~ WidthT1 + Sow_To_Flower + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ Sow_To_Flower)),
      method = "REML",
      data = SEM.Data),
  
  # M3
  lme(NflowT2 ~ Sow_To_Flower + WidthT1 + WidthT2 + NflowT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = SEM.Data),
  
  # M4
  lme(WidthT2 ~ HeightT1 + Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = SEM.Data),
  
  # M5
  lme(HeightT1 ~ Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      method = "REML",
      data = SEM.Data),
  
  # M6
  lme(HeightT2 ~ Sow_To_Flower + WidthT2 + HeightT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = SEM.Data),
  
  # M7
  lme(TotalPollinators ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year,
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = SEM.Data),
  
  # M8
  lme(FPP ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = SEM.Data),
  
  # M9
  lme(Nseeds ~ NflowT2 + HeightT2 + WidthT2 + FPP + TotalPollinators +  Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),
                        varPower(form =~ WidthT2)),
      method = "REML",
      data = SEM.Data),
  
  # Correlated errors
  NflowT1 %~~% HeightT1,
  NflowT2 %~~% HeightT2,
  FPP %~~% TotalPollinators
)
(Overall.Summary <- summary(Causal.H)) 
```

## 2.2 Control

```{r, Control causal hypothesis}
# Subset data
C.Data <- subset(SEM.Data, Treatment == "C")

# Fit the PSEM
Causal.H.C <- psem(
  # M1
  lme(Sow_To_Flower ~ WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = C.Data),
  
  # M2
  lme(NflowT1 ~ WidthT1 + Sow_To_Flower + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ Sow_To_Flower)),
      method = "REML",
      data = C.Data),
  
  # M3
  lme(NflowT2 ~ Sow_To_Flower + WidthT1 + WidthT2 + NflowT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = C.Data),
  
  # M4
  lme(WidthT2 ~ HeightT1 + Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = C.Data),
  
  # M5
  lme(HeightT1 ~ Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      method = "REML",
      data = C.Data),
  
  # M6
  lme(HeightT2 ~ Sow_To_Flower + WidthT2 + HeightT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = C.Data),
  
  # M7
  lme(TotalPollinators ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year,
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = C.Data),
  
  # M8
  lme(FPP ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = C.Data),
  
  # M9
  lme(Nseeds ~ NflowT2 + HeightT2 + WidthT2 + FPP + TotalPollinators +  Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),
                        varPower(form =~ WidthT2)),
      method = "REML",
      data = C.Data),
  
  # Correlated errors
  NflowT1 %~~% HeightT1,
  NflowT2 %~~% HeightT2,
  FPP %~~% TotalPollinators
)
(C.Summary <- summary(Causal.H.C)) 
```

## 2.3 Chitin

```{r, Chitin causal hypothesis}
# Subset data
CHT.Data <- subset(SEM.Data, Treatment == "CHT")

# Fit the PSEM
Causal.H.CHT <- psem(
  # M1
  lme(Sow_To_Flower ~ WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = CHT.Data),
  
  # M2
  lme(NflowT1 ~ WidthT1 + Sow_To_Flower + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ Sow_To_Flower)),
      method = "REML",
      data = CHT.Data),
  
  # M3
  lme(NflowT2 ~ Sow_To_Flower + WidthT1 + WidthT2 + NflowT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = CHT.Data),
  
  # M4
  lme(WidthT2 ~ HeightT1 + Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = CHT.Data),
  
  # M5
  lme(HeightT1 ~ Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      method = "REML",
      data = CHT.Data),
  
  # M6
  lme(HeightT2 ~ Sow_To_Flower + WidthT2 + HeightT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = CHT.Data),
  
  # M7
  lme(TotalPollinators ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year,
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = CHT.Data),
  
  # M8
  lme(FPP ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = CHT.Data),
  
  # M9
  lme(Nseeds ~ NflowT2 + HeightT2 + WidthT2 + FPP + TotalPollinators +  Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),
                        varPower(form =~ WidthT2)),
      method = "REML",
      data = CHT.Data),
  
  # Correlated errors
  NflowT1 %~~% HeightT1,
  NflowT2 %~~% HeightT2,
  FPP %~~% TotalPollinators
)
(CHT.Summary <- summary(Causal.H.CHT)) 
```

## 2.4 Organic fertilizer

```{r, Organic fertilizer causal hypothesis}
# Subset data
OF.Data <- subset(SEM.Data, Treatment == "OF")

# Fit the PSEM
Causal.H.OF <- psem(
  # M1
  lme(Sow_To_Flower ~ WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = OF.Data),
  
  # M2
  lme(NflowT1 ~ WidthT1 + Sow_To_Flower + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ Sow_To_Flower)),
      method = "REML",
      data = OF.Data),
  
  # M3
  lme(NflowT2 ~ Sow_To_Flower + WidthT1 + WidthT2 + NflowT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = OF.Data),
  
  # M4
  lme(WidthT2 ~ HeightT1 + Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = OF.Data),
  
  # M5
  lme(HeightT1 ~ Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      method = "REML",
      data = OF.Data),
  
  # M6
  lme(HeightT2 ~ Sow_To_Flower + WidthT2 + HeightT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = OF.Data),
  
  # M7
  lme(TotalPollinators ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year,
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = OF.Data),
  
  # M8
  lme(FPP ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = OF.Data),
  
  # M9
  lme(Nseeds ~ NflowT2 + HeightT2 + WidthT2 + FPP + TotalPollinators +  Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),
                        varPower(form =~ WidthT2)),
      method = "REML",
      data = OF.Data),
  
  # Correlated errors
  NflowT1 %~~% HeightT1,
  NflowT2 %~~% HeightT2,
  FPP %~~% TotalPollinators
)
(OF.Summary <- summary(Causal.H.OF)) 
```

## 2.5 House Cricket

```{r, House Cricket causal hypothesis}
# Subset data
HC.Data <- subset(SEM.Data, Treatment == "HC")

# Fit the PSEM
Causal.H.HC <- psem(
  # M1
  lme(Sow_To_Flower ~ WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = HC.Data),
  
  # M2
  lme(NflowT1 ~ WidthT1 + Sow_To_Flower + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ Sow_To_Flower)),
      method = "REML",
      data = HC.Data),
  
  # M3
  lme(NflowT2 ~ Sow_To_Flower + WidthT1 + WidthT2 + NflowT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = HC.Data),
  
  # M4
  lme(WidthT2 ~ HeightT1 + Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = HC.Data),
  
  # M5
  lme(HeightT1 ~ Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      method = "REML",
      data = HC.Data),
  
  # M6
  lme(HeightT2 ~ Sow_To_Flower + WidthT2 + HeightT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = HC.Data),
  
  # M7
  lme(TotalPollinators ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year,
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = HC.Data),
  
  # M8
  lme(FPP ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = HC.Data),
  
  # M9
  lme(Nseeds ~ NflowT2 + HeightT2 + WidthT2 + FPP + TotalPollinators +  Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),
                        varPower(form =~ WidthT2)),
      method = "REML",
      data = HC.Data),
  
  # Correlated errors
  NflowT1 %~~% HeightT1,
  NflowT2 %~~% HeightT2,
  FPP %~~% TotalPollinators
)
(HC.Summary <- summary(Causal.H.HC)) 
```

## 2.6 Black Soldier Fly

```{r, Black Soldier Fly causal hypothesis}
# Subset data
BSF.Data <- subset(SEM.Data, Treatment == "BSF")

# Fit the PSEM
Causal.H.BSF <- psem(
  # M1
  lme(Sow_To_Flower ~ WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = BSF.Data),
  
  # M2
  lme(NflowT1 ~ WidthT1 + Sow_To_Flower + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ Sow_To_Flower)),
      method = "REML",
      data = BSF.Data),
  
  # M3
  lme(NflowT2 ~ Sow_To_Flower + WidthT1 + WidthT2 + NflowT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = BSF.Data),
  
  # M4
  lme(WidthT2 ~ HeightT1 + Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = BSF.Data),
  
  # M5
  lme(HeightT1 ~ Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      method = "REML",
      data = BSF.Data),
  
  # M6
  lme(HeightT2 ~ Sow_To_Flower + WidthT2 + HeightT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = BSF.Data),
  
  # M7
  lme(TotalPollinators ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year,
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = BSF.Data),
  
  # M8
  lme(FPP ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = BSF.Data),
  
  # M9
  lme(Nseeds ~ NflowT2 + HeightT2 + WidthT2 + FPP + TotalPollinators +  Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),
                        varPower(form =~ WidthT2)),
      method = "REML",
      data = BSF.Data),
  
  # Correlated errors
  NflowT1 %~~% HeightT1,
  NflowT2 %~~% HeightT2,
  FPP %~~% TotalPollinators
)
(BSF.Summary <- summary(Causal.H.BSF)) 
```

## 2.7 Mealworm

```{r, Mealworm causal hypothesis}
# Subset data
MW.Data <- subset(SEM.Data, Treatment == "MW")

# Fit the PSEM
Causal.H.MW <- psem(
  # M1
  lme(Sow_To_Flower ~ WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = MW.Data),
  
  # M2
  lme(NflowT1 ~ WidthT1 + Sow_To_Flower + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ Sow_To_Flower)),
      method = "REML",
      data = MW.Data),
  
  # M3
  lme(NflowT2 ~ Sow_To_Flower + WidthT1 + WidthT2 + NflowT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = MW.Data),
  
  # M4
  lme(WidthT2 ~ HeightT1 + Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = MW.Data),
  
  # M5
  lme(HeightT1 ~ Sow_To_Flower + WidthT1 + Year, 
      random = list(Block_Code = ~ 1),
      method = "REML",
      data = MW.Data),
  
  # M6
  lme(HeightT2 ~ Sow_To_Flower + WidthT2 + HeightT1 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = MW.Data),
  
  # M7
  lme(TotalPollinators ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year,
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),varExp(form =~ WidthT2)),
      method = "REML",
      data = MW.Data),
  
  # M8
  lme(FPP ~ Sow_To_Flower + NflowT1 + NflowT2 + HeightT1 + HeightT2 + Year, 
      random = list(Block_Code = ~ 1),
      weights = varIdent(form = ~ 1 | Year),
      method = "REML",
      data = MW.Data),
  
  # M9
  lme(Nseeds ~ NflowT2 + HeightT2 + WidthT2 + FPP + TotalPollinators +  Year, 
      random = list(Block_Code = ~ 1),
      weights = varComb(varIdent(form = ~ 1 | Year),
                        varPower(form =~ WidthT2)),
      method = "REML",
      data = MW.Data),
  
  # Correlated errors
  NflowT1 %~~% HeightT1,
  NflowT2 %~~% HeightT2,
  FPP %~~% TotalPollinators
)
(MW.Summary <- summary(Causal.H.MW)) 
```


# 3. Effects on seed set

## 3.1 Extract path coefficients
```{r, extract path coefficients}
Not.Causal.Paths <- c("Year",
                     "Year = 2020",
                     "Year = 2021",
                     "~~HeightT1",
                     "~~HeightT2",
                     "~~TotalPollinators")

# Control dataset
Paths.Control <- subset(as.data.frame(C.Summary$coefficients), 
                        Predictor %notin% Not.Causal.Paths)
Paths.Control$Treatment <- "C"
Paths.Control$Pathway <- interaction(Paths.Control$Response, Paths.Control$Predictor)

Numerics <- c("Estimate","Std.Error","Std.Estimate")
Factors <- c("Response","Predictor","Treatment", "Pathway")
Paths.Control[Numerics] <- lapply(Paths.Control[Numerics], as.numeric)
Paths.Control[Factors] <- lapply(Paths.Control[Factors], factor)

# Chitin paths
Paths.Chitin <- subset(as.data.frame(CHT.Summary$coefficients), 
                       Predictor %notin% Not.Causal.Paths)
Paths.Chitin$Treatment <- "CHT"
Paths.Chitin$Pathway <- interaction(Paths.Chitin$Response, Paths.Chitin$Predictor)

# Organic Fertilizer paths
Paths.Organic <- subset(as.data.frame(OF.Summary$coefficients), 
                        Predictor %notin% Not.Causal.Paths)
Paths.Organic$Treatment <- "OF"
Paths.Organic$Pathway <- interaction(Paths.Organic$Response, Paths.Organic$Predictor)

# Cricket paths
Paths.HC_Amended <- subset(as.data.frame(HC.Summary$coefficients), 
                           Predictor %notin% Not.Causal.Paths)
Paths.HC_Amended$Treatment <- "HC"
Paths.HC_Amended$Pathway <- interaction(Paths.HC_Amended$Response, Paths.HC_Amended$Predictor)

# BSF paths
Paths.BSF_Amended <- subset(as.data.frame(BSF.Summary$coefficients), 
                            Predictor %notin% Not.Causal.Paths)
Paths.BSF_Amended$Treatment <- "BSF"
Paths.BSF_Amended$Pathway <- interaction(Paths.BSF_Amended$Response, Paths.BSF_Amended$Predictor)
# MW paths
Paths.MW_Amended <- subset(as.data.frame(MW.Summary$coefficients), 
                           Predictor %notin% Not.Causal.Paths)
Paths.MW_Amended$Treatment <- "MW"
Paths.MW_Amended$Pathway <- interaction(Paths.MW_Amended$Response, Paths.MW_Amended$Predictor)


# Note: We are keeping the control paths in a separate dataframe as the other treatments, as the causal effects observed for control plants will serve as the baseline.

Combined.results <- rbind(Paths.Chitin,
                          Paths.Organic,
                          Paths.HC_Amended,
                          Paths.BSF_Amended,
                          Paths.MW_Amended)


Combined.results[Numerics] <- lapply(Combined.results[Numerics], as.numeric)
Combined.results[Factors] <- lapply(Combined.results[Factors], factor)

Combined.results$Treatment <- factor(Combined.results$Treatment, 
                                     levels = c("CHT", "OF", 
                                                "BSF", "HC","MW"))

```


## 3.2 Calculate effects
```{r, calculate effects on seed production}

# First specify this for control plants
# FPP 
FPP_Direct <- Paths.Control[which(Paths.Control$Pathway == "Nseeds.FPP"),]$Std.Estimate
FPP_Indirect <- 0
FPP_Total <- FPP_Direct + FPP_Indirect

# N pollinators 
Total_Poll_Direct <- Paths.Control[which(Paths.Control$Pathway == "Nseeds.TotalPollinators"),]$Std.Estimate
Total_Poll_Indirect <- 0
Total_Poll_Total <- Total_Poll_Direct + Total_Poll_Indirect

# Height T2
HT2_Direct <- Paths.Control[which(Paths.Control$Pathway == "Nseeds.HeightT2"),]$Std.Estimate
HT2_Indirect <- 
  # Path over FPP 
  Paths.Control[which(Paths.Control$Pathway == "FPP.HeightT2"),]$Std.Estimate * FPP_Direct +
  # Path over Total_Poll
  Paths.Control[which(Paths.Control$Pathway == "TotalPollinators.HeightT2"),]$Std.Estimate * Total_Poll_Direct
HT2_Total <- HT2_Direct + HT2_Indirect

# NFlowers T2
NFT2_Direct <- Paths.Control[which(Paths.Control$Pathway == "Nseeds.NflowT2"),]$Std.Estimate
NFT2_Indirect <- 
  # Path over FPP 
  Paths.Control[which(Paths.Control$Pathway == "FPP.NflowT2"),]$Std.Estimate * FPP_Direct +
  # Path over Total_Poll
  Paths.Control[which(Paths.Control$Pathway == "TotalPollinators.NflowT2"),]$Std.Estimate * Total_Poll_Direct
NFT2_Total <- NFT2_Direct + NFT2_Indirect

# Width T2
WT2_Direct <- Paths.Control[which(Paths.Control$Pathway == "Nseeds.WidthT2"),]$Std.Estimate
WT2_Indirect <- 
  # Path over Height T2 
  Paths.Control[which(Paths.Control$Pathway == "HeightT2.WidthT2"),]$Std.Estimate * HT2_Direct +
  # Path over NFlowers T2
  Paths.Control[which(Paths.Control$Pathway == "NflowT2.WidthT2"),]$Std.Estimate * NFT2_Direct
WT2_Total <- WT2_Direct + WT2_Indirect

# NFlowers T1
NFT1_Direct <- 0 
NFT1_Indirect <- 
  # Path over N_Flowers T2
  Paths.Control[which(Paths.Control$Pathway == "NflowT2.NflowT1"),]$Std.Estimate * NFT2_Direct +
  # Path over FPP
  Paths.Control[which(Paths.Control$Pathway == "FPP.NflowT1"),]$Std.Estimate * FPP_Direct +
  # Path over Total Pollinators
  Paths.Control[which(Paths.Control$Pathway == "TotalPollinators.NflowT1"),]$Std.Estimate * Total_Poll_Direct
NFT1_Total <- NFT1_Direct + NFT1_Indirect

# Height T1
HT1_Direct <- 0
HT1_Indirect <- 
  # Path over Height  T2
  Paths.Control[which(Paths.Control$Pathway == "HeightT2.HeightT1"),]$Std.Estimate * HT2_Total + 
  # Path over Width T2 
  Paths.Control[which(Paths.Control$Pathway == "WidthT2.HeightT1"),]$Std.Estimate * WT2_Total +
  # Path over FPP
  Paths.Control[which(Paths.Control$Pathway == "FPP.HeightT1"),]$Std.Estimate * FPP_Direct +
  # Path over Total Pollinators
  Paths.Control[which(Paths.Control$Pathway == "TotalPollinators.HeightT1"),]$Std.Estimate * Total_Poll_Direct  

HT1_Total <- HT1_Direct + HT1_Indirect


# Sow To Flower

STF_Direct <- 0
STF_Indirect <- 
  # Path over Height  T2
  Paths.Control[which(Paths.Control$Pathway == "HeightT2.Sow_To_Flower"),]$Std.Estimate * HT2_Total +
  # Path over Width  T2
  Paths.Control[which(Paths.Control$Pathway == "WidthT2.Sow_To_Flower"),]$Std.Estimate * WT2_Total +
  # Path over N Flowers  T2
  Paths.Control[which(Paths.Control$Pathway == "NflowT2.Sow_To_Flower"),]$Std.Estimate * NFT2_Total +
  # Path over Height  T1
  Paths.Control[which(Paths.Control$Pathway == "HeightT1.Sow_To_Flower"),]$Std.Estimate * HT1_Total +
  # Path over N Flowers  T1
  Paths.Control[which(Paths.Control$Pathway == "NflowT1.Sow_To_Flower"),]$Std.Estimate * NFT1_Total +
  # Path over FPP
  Paths.Control[which(Paths.Control$Pathway == "FPP.Sow_To_Flower"),]$Std.Estimate * FPP_Direct +
  # Path over Total Pollinators
  Paths.Control[which(Paths.Control$Pathway == "TotalPollinators.Sow_To_Flower"),]$Std.Estimate * Total_Poll_Direct

STF_Total <- STF_Direct + STF_Indirect

# Width T1

WT1_Direct <- 0
WT1_Indirect <- 
  # Path over Height T1
  Paths.Control[which(Paths.Control$Pathway == "HeightT1.WidthT1"),]$Std.Estimate * HT1_Total +
  # Path over N Flowers T1
  Paths.Control[which(Paths.Control$Pathway == "NflowT1.WidthT1"),]$Std.Estimate * NFT1_Total +
  # Path over N Flowers T2
  Paths.Control[which(Paths.Control$Pathway == "NflowT2.WidthT1"),]$Std.Estimate * NFT2_Total +
  # Path over Width T2
  Paths.Control[which(Paths.Control$Pathway == "WidthT2.WidthT1"),]$Std.Estimate * WT2_Total +
  # Path over Sow to Flower
  Paths.Control[which(Paths.Control$Pathway == "Sow_To_Flower.WidthT1"),]$Std.Estimate * STF_Total


WT1_Total <- WT1_Direct + WT1_Indirect

Control_Effects <- rbind(WT1_Total,
                         STF_Total,
                         HT1_Total,
                         NFT1_Total,
                         WT2_Total,
                         HT2_Total,
                         NFT2_Total,
                         FPP_Total,
                         Total_Poll_Total)


# Now for the other treatments, using a loop

All_Effects <- data.frame("C" = Control_Effects)

Treatmen_Levels <- levels(Combined.results$Treatment)

for (i in 1:length(Treatmen_Levels)){
  Path_Data <- subset(Combined.results, Treatment == Treatmen_Levels[i])
  
  # Effects of each variable on seed production
  
  # FPP 
  FPP_Direct <- Path_Data[which(Path_Data$Pathway == "Nseeds.FPP"),]$Std.Estimate
  FPP_Indirect <- 0
  FPP_Total <- FPP_Direct + FPP_Indirect
  
  # N pollinators 
  Total_Poll_Direct <- Path_Data[which(Path_Data$Pathway == "Nseeds.TotalPollinators"),]$Std.Estimate
  Total_Poll_Indirect <- 0
  Total_Poll_Total <- Total_Poll_Direct + Total_Poll_Indirect
  
  # Height T2
  HT2_Direct <- Path_Data[which(Path_Data$Pathway == "Nseeds.HeightT2"),]$Std.Estimate
  HT2_Indirect <- 
    # Path over FPP 
    Path_Data[which(Path_Data$Pathway == "FPP.HeightT2"),]$Std.Estimate * FPP_Direct +
    # Path over Total_Poll
    Path_Data[which(Path_Data$Pathway == "TotalPollinators.HeightT2"),]$Std.Estimate * Total_Poll_Direct
  HT2_Total <- HT2_Direct + HT2_Indirect
  
  # NFlowers T2
  NFT2_Direct <- Path_Data[which(Path_Data$Pathway == "Nseeds.NflowT2"),]$Std.Estimate
  NFT2_Indirect <- 
    # Path over FPP 
    Path_Data[which(Path_Data$Pathway == "FPP.NflowT2"),]$Std.Estimate * FPP_Direct +
    # Path over Total_Poll
    Path_Data[which(Path_Data$Pathway == "TotalPollinators.NflowT2"),]$Std.Estimate * Total_Poll_Direct
  NFT2_Total <- NFT2_Direct + NFT2_Indirect
  
  # Width T2
  WT2_Direct <- Path_Data[which(Path_Data$Pathway == "Nseeds.WidthT2"),]$Std.Estimate
  WT2_Indirect <- 
    # Path over Height T2 
    Path_Data[which(Path_Data$Pathway == "HeightT2.WidthT2"),]$Std.Estimate * HT2_Direct +
    # Path over NFlowers T2
    Path_Data[which(Path_Data$Pathway == "NflowT2.WidthT2"),]$Std.Estimate * NFT2_Direct
  WT2_Total <- WT2_Direct + WT2_Indirect
  
  # NFlowers T1
  NFT1_Direct <- 0 
  NFT1_Indirect <- 
    # Path over N_Flowers T2
    Path_Data[which(Path_Data$Pathway == "NflowT2.NflowT1"),]$Std.Estimate * NFT2_Direct +
    # Path over FPP
    Path_Data[which(Path_Data$Pathway == "FPP.NflowT1"),]$Std.Estimate * FPP_Direct +
    # Path over Total Pollinators
    Path_Data[which(Path_Data$Pathway == "TotalPollinators.NflowT1"),]$Std.Estimate * Total_Poll_Direct
  NFT1_Total <- NFT1_Direct + NFT1_Indirect
  
  # Height T1
  HT1_Direct <- 0
  HT1_Indirect <- 
    # Path over Height  T2
    Path_Data[which(Path_Data$Pathway == "HeightT2.HeightT1"),]$Std.Estimate * HT2_Total + 
    # Path over Width T2 
    Path_Data[which(Path_Data$Pathway == "WidthT2.HeightT1"),]$Std.Estimate * WT2_Total +
    # Path over FPP
    Path_Data[which(Path_Data$Pathway == "FPP.HeightT1"),]$Std.Estimate * FPP_Direct +
    # Path over Total Pollinators
    Path_Data[which(Path_Data$Pathway == "TotalPollinators.HeightT1"),]$Std.Estimate * Total_Poll_Direct  
  
  HT1_Total <- HT1_Direct + HT1_Indirect
  
  
  # Sow To Flower
  
  STF_Direct <- 0
  STF_Indirect <- 
    # Path over Height  T2
    Path_Data[which(Path_Data$Pathway == "HeightT2.Sow_To_Flower"),]$Std.Estimate * HT2_Total +
    # Path over Width  T2
    Path_Data[which(Path_Data$Pathway == "WidthT2.Sow_To_Flower"),]$Std.Estimate * WT2_Total +
    # Path over N Flowers  T2
    Path_Data[which(Path_Data$Pathway == "NflowT2.Sow_To_Flower"),]$Std.Estimate * NFT2_Total +
    # Path over Height  T1
    Path_Data[which(Path_Data$Pathway == "HeightT1.Sow_To_Flower"),]$Std.Estimate * HT1_Total +
    # Path over N Flowers  T1
    Path_Data[which(Path_Data$Pathway == "NflowT1.Sow_To_Flower"),]$Std.Estimate * NFT1_Total +
    # Path over FPP
    Path_Data[which(Path_Data$Pathway == "FPP.Sow_To_Flower"),]$Std.Estimate * FPP_Direct +
    # Path over Total Pollinators
    Path_Data[which(Path_Data$Pathway == "TotalPollinators.Sow_To_Flower"),]$Std.Estimate * Total_Poll_Direct
  
  STF_Total <- STF_Direct + STF_Indirect
  
  
  # Width T1
  WT1_Direct <- 0
  WT1_Indirect <- 
    # Path over Height T1
    Path_Data[which(Path_Data$Pathway == "HeightT1.WidthT1"),]$Std.Estimate * HT1_Total +
    # Path over N Flowers T1
    Path_Data[which(Path_Data$Pathway == "NflowT1.WidthT1"),]$Std.Estimate * NFT1_Total +
    # Path over N Flowers T2
    Path_Data[which(Path_Data$Pathway == "NflowT2.WidthT1"),]$Std.Estimate * NFT2_Total +
    # Path over Width T2
    Path_Data[which(Path_Data$Pathway == "WidthT2.WidthT1"),]$Std.Estimate * WT2_Total +
    # Path over Sow to Flower
    Path_Data[which(Path_Data$Pathway == "Sow_To_Flower.WidthT1"),]$Std.Estimate * STF_Total

  WT1_Total <- WT1_Direct + WT1_Indirect
  
  Path_Effects <- as.data.frame(rbind(WT1_Total,
                                      STF_Total,
                                      HT1_Total,
                                      NFT1_Total,
                                      WT2_Total,
                                      HT2_Total,
                                      NFT2_Total,
                                      FPP_Total,
                                      Total_Poll_Total))
  
  colnames(Path_Effects) <- Treatmen_Levels[i]
  
  All_Effects <- cbind(All_Effects,Path_Effects)
  
}

```

## 3.3 Plot effects in heatmap

```{r, Heatmap}

Stacked_Effects <- data.frame("Treatment" = as.data.frame(stack(All_Effects))$ind,
                              "Path" = c("SowToFlower","WidthT1","HeightT1","NFlowersT1",
                                         "WidthT2","HeightT2","NFlowersT2","FPP","Total_Poll_Total"),
                              "TotalEffect" = as.data.frame(stack(All_Effects))$values)


Stacked_Effects$Path <- factor(Stacked_Effects$Path, 
                               levels = c("SowToFlower","WidthT1","HeightT1","NFlowersT1",
                                          "WidthT2","HeightT2","NFlowersT2","FPP","Total_Poll_Total"))

Stacked_Effects$Treatment <- factor(Stacked_Effects$Treatment, 
                               levels = c("C", "HC", "BSF", "MW", "CHT", "OF"))


ggplot(data = Stacked_Effects, aes(x = Treatment, y = Path, fill = TotalEffect)) +
  geom_tile() +
  geom_text(aes(label = format(round(TotalEffect,2), nsmall = 2))) +
  scale_fill_gradient2(name = "Effect on seed set",
                       low = "#A51122",
                       mid = "#FFFFFF",
                       high = "#006228",
                       limits = c(-1, 1), 
                       breaks = seq(-1,1,by=0.25)) + 
  scale_y_discrete(labels = c("SowToFlower" = "Time until flowering",
                              "WidthT1" = "Width T1",
                              "HeightT1" = "Heigh T1",
                              "NFlowersT1" = "Number of flowers T1", 
                              "WidthT2" = "Width T2",
                              "HeightT2" = "Heigh T2",
                              "NFlowersT2" = "Number of flowers T2",
                              "FPP" = "Flowers visited per pollinator",
                              "Total_Poll_Total" = "Total number of pollinators")) +
  labs(y = " ") +
  CustomPlot
```
